\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{times}


\cvprfinalcopy % *** Uncomment this line for the final submission
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\usepackage{indentfirst}
\setlength{\parindent}{2em}
\usepackage{cite}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,backref=page]{hyperref}

\author{Xuewen Yang\\\\
August 3 2018}

\title{Improving Object Detection with Deep Convolutional Networks via Bayesian Optimization and Structured Prediction}
 
\begin{document}
\maketitle
\begin{abstract}
Object detection systems based on the deep convolutional neural network (CNN) have recently made groundbreaking advances on several object detection benchmarks.While the features learned by these high-capacity neural networks are discriminative for categorization, inaccurate localization is still a major source of error for detection.Building upon high-capacity CNN architectures,the author address the localization problem by 1) using a search algorithm based on Bayesian optimization that sequentially proposes candidate regions for an object bounding box, and 2) training the CNN with a structured loss that explicitly penalizes the localization inaccuracy. In experiments, they demonstrate that each of the proposed methods improves the detection performance over the baseline method on PASCAL VOC 2007 and 2012 datasets. Furthermore, two
methods are complementary and significantly outperform the previous state-of-the-art when combined.
\end{abstract}
\section{Introduction}
Object detection is one of the long-standing and important
problems in computer vision. Motivated by the recent
success of deep learning\cite{Bengio2007Greedy}\cite{Ranzato2007Sparse}\cite{Bengio2013Representation} on visual
object recognition tasks, significant
improvements have been made in the object detection
problem. Most notably, Girshick~\emph{et al.}
proposed the ¡°regions with convolutional neural network¡±
(R-CNN) framework for object detection and demonstrated
state-of-the-art performance on standard detection benchmarks
(e.g., PASCAL VOC, ILSVRC) with a
large margin over the previous arts, which are mostly based
on deformable part model (DPM)\cite{Felzenszwalb2010Object}.

There are two major keys to the success of the R-CNN.
First, features matter. In the R-CNN, the low-level
image features (e.g., HOG\cite{Dalal2005Histograms}) are replaced with the CNN
features, which are arguably more discriminative representations.
One drawback of CNN features, however, is that
they are expensive to compute. The R-CNN overcomes this
issue by proposing a few hundreds or thousands candidate bounding boxes via the selective search algorithm [44] to
effectively reduce the computational cost required to evaluate
the detection scores at all regions of an image.

Despite the success of R-CNN, it has been pointed out
through an error analysis that inaccurate localization
causes the most egregious errors in the R-CNN framework. For example, if there is no bounding box in the
close proximity of ground truth among those proposed by
selective search, no matter what we have for the features
or classifiers, there is no way to detect the correct bounding
box of the object. Indeed, there are many applications
that require accurate localization of an object bounding box,
such as detecting moving objects (e.g., car, pedestrian, bicycles)
for autonomous driving\cite{Geiger2012Are}, detecting objects for
robotic grasping or manipulation in robotic surgery or manufacturing, and many others.
\section{Fine-grained search for bounding box via Bayesian optimization}
In this section, the author develop a fine-grained search (FGS) algorithm based on Bayesian optimization that sequentially proposes a new bounding
box with a higher expected detection score than previously proposed bounding boxes without significantly increasing number of region proposals.
\subsection{General Bayesian optimization framework}
In the Bayesian optimization framework, $f=f(x; y)$ is assumed to be drawn from a probabilistic model:$ p(f|D_N)\infty p(D_N|f)p(f)$.Bayesian optimization is efficient in terms of the number
of function evaluation [24], and is particularly effective
when f is computationally expensive.
\subsection{Local finegrained search}
In this section, the author extend the GPR-based algorithm for
global maximum search to local fine-grained search (FGS).They perform
the FGS by pruning out easy negatives with low classification
scores from the set of regions proposed by the
selective search algorithm and sorting out a few bounding
boxes with the maximum scores in local regions. Then, for
each local optimum $y_{best}$, they propose
a new candidate bounding box.Specifically, they initialize a set of local observations $D_{local}$
for $y_{best}$ from the set given by the selective search algorithm,
whose localness is measured by an IoU between $y_{best}$ and region
proposals.
{\small
\bibliographystyle{ieee}
\bibliography{1}
}

\end{document}
